---
title: "fcc-licensees"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Purpose

To create a list of licensed hams in the State College area for use by the Nittany Amateur Radio Club's outreach and communication efforts.

# Gathering

Data were gathered for licenses active in the last two years from the FCC ULS database:

<https://wireless2.fcc.gov/UlsApp/UlsSearch/searchAmateur.jsp>

The 16801, 16802, and 16803 zip codes were selected.

Once the FCC database provided URLs, these 'pipe'-delimited data files were downloaded. The raw files are in `data/pipe`.

```{r}
data_dir <- 'data/pipe'
```


# Cleaning
  
## Import

I will focus on the `*all-16801.txt` and `*all-16803.txt` files since these are larger and more comprehensive.

```{r}
hams_801 <- read.delim(file = paste0(data_dir, '/fcc-ham-all-16801.txt'), sep = '|', header = FALSE)
```

The file is a mess.
Callsigns are mixed up with dates. There must be some problem in the parsing.
I opened the file in a text editor, changed the pipes to tabs, and trimmed the file to include the names and addresses, and saved it in `data/tab/`.

```{r}
hams_801 <- read.delim(file = 'data/tab/16801-trim.txt', header = FALSE)
str(hams_801)
```

This looks a little better.
I'm going to keep the callsigns, name info, and address.

```{r}
trimmed_801 <- hams_801 %>%
  select(., V5, V8, V9, V10, V11, V12, V16, V17, V18, V19, V23)
trimmed_801 %>% 
  knitr::kable()
```

I say we can keep V5, V8, V16, V17, V18, and V19, and drop the rest.

```{r}
hams_16801 <- trimmed_801 %>%
  select(., V5, V8, V16, V17, V18, V19) %>%
  rename(., callsign = V5, name = V8, address = V16, city = V17, state = V18, zip = V19) %>%
  arrange(by = callsign)
hams_16801 %>% knitr::kable(.)
```
 
 That looks good.
 Now let's try the same thing with the 16803 file.
 
I manually trimmed the 16803 file.

```{r}
hams_803 <- read.delim(file = 'data/tab/16803-trim.txt', header = FALSE)
str(hams_803)
```

```{r}
trimmed_803 <- hams_803 %>%
  select(., V5, V8, V9, V10, V11, V12, V16, V17, V18, V19, V23)
trimmed_803 %>% knitr::kable(.)
```

```{r}
hams_16803 <- trimmed_803 %>%
  select(., V5, V8, V16, V17, V18, V19) %>%
  rename(., callsign = V5, name = V8, address = V16, city = V17, state = V18, zip = V19) %>%
  arrange(by = callsign)
hams_16803 %>% 
  knitr::kable(.)
```

Now, we should be able to merge them.

```{r}
hams_01_03 <- rbind(hams_16801, hams_16803)
hams_01_03 <- hams_01_03 %>%
  arrange(by = callsign)
hams_01_03 %>% 
  knitr::kable()
```

# Next steps

1. Normalize the address, city, and zip fields.
2. Automate queries to the FCC database.
3. Expand the range of licensees.
4. Focus on new licensees (last year?)
