---
title: "fcc-licensees"
author: "Rick O. Gilmore"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Purpose

To create a list of licensed hams in the State College area for use by the Nittany Amateur Radio Club's outreach and communication efforts.

# Gathering

Data were gathered for licenses active in the last two years from the FCC ULS database:

<https://wireless2.fcc.gov/UlsApp/UlsSearch/searchAmateur.jsp>


## Search Criteria

Operator Class: All

State: Pennsylvania

ZIP code: 

A list of zip codes in Centre County can be found here:

<http://ciclt.net/sn/clt/capitolimpact/gw_ziplist.aspx?ClientCode=capitolimpact&State=pa&StName=Pennsylvania&StFIPS=42&FIPS=42027>

On 2019-04-30 I ran 16823. 

The 16801, 16802, and 16803 zip codes were run previously.

License Detail: Status: Active

Date Information:
    Date Type: Last Action Date
    Date: From 4/30/2010 to 4/30/2019
    
## Retrieving search results

Clicking on the `Query Download` button opens a page where an email can be given.
The email will be sent a download link when the search file is ready.
Once the FCC database provided URLs, these 'pipe'-delimited data files were downloaded. The raw files are in `data/pipe`.

```{r}
data_dir <- 'data/pipe'
```

# Cleaning
  
## Import

### 16801

```{r}
hams_801 <- read.delim(file = paste0(data_dir, '/fcc-ham-all-16801.txt'), sep = '|', header = FALSE)
```

The file is a mess.
Callsigns are mixed up with dates. There must be some problem in the parsing.
I opened the file in a text editor, changed the pipes to tabs, and trimmed the file to include the names and addresses, and saved it in `data/tab/`.

```{r}
hams_801 <- read.delim(file = 'data/tab/16801-trim.txt', header = FALSE)
str(hams_801)
```

This looks a little better.
I'm going to keep the callsigns, name info, and address.

```{r}
trimmed_801 <- hams_801 %>%
  select(., V5, V8, V9, V10, V11, V12, V16, V17, V18, V19, V23)
trimmed_801 %>% 
  knitr::kable()
```

I say we can keep V5, V8, V16, V17, V18, and V19, and drop the rest.

```{r}
hams_16801 <- trimmed_801 %>%
  select(., V5, V8, V16, V17, V18, V19) %>%
  rename(., callsign = V5, name = V8, address = V16, city = V17, state = V18, zip = V19) %>%
  arrange(by = callsign)
hams_16801 %>% knitr::kable(.)
```
 
 That looks good.
 
### 16803
 
Now let's try the same thing with the 16803 file.
 
I manually trimmed the 16803 file.

```{r}
hams_803 <- read.delim(file = 'data/tab/16803-trim.txt', header = FALSE)
str(hams_803)
```

```{r}
trimmed_803 <- hams_803 %>%
  select(., V5, V8, V9, V10, V11, V12, V16, V17, V18, V19, V23)
trimmed_803 %>% knitr::kable(.)
```

```{r}
hams_16803 <- trimmed_803 %>%
  select(., V5, V8, V16, V17, V18, V19) %>%
  rename(., callsign = V5, name = V8, address = V16, city = V17, state = V18, zip = V19) %>%
  arrange(by = callsign)
hams_16803 %>% 
  knitr::kable(.)
```

Now, we should be able to merge them.

```{r}
hams_01_03 <- rbind(hams_16801, hams_16803)
hams_01_03 <- hams_01_03 %>%
  arrange(by = callsign)
hams_01_03 %>% 
  knitr::kable()
```

### 16823

Let's try this with 16823 (Bellefonte).

```{r}
hams_823 <- read.delim(file = 'data/tab/16823-trim.txt', header = FALSE)
str(hams_823)
```

```{r}
trimmed_823 <- hams_823 %>%
  select(., V5, V8, V9, V10, V11, V12, V16, V17, V18, V19, V23)
trimmed_823 %>% knitr::kable(.)
```

```{r}
hams_16823 <- trimmed_823 %>%
  select(., V5, V8, V16, V17, V18, V19) %>%
  rename(., callsign = V5, name = V8, address = V16, city = V17, state = V18, zip = V19) %>%
  arrange(by = callsign)
hams_16823 %>% 
  knitr::kable(.)
```

### 16802

```{r}
hams <- read.delim(file = 'data/tab/16802-trim.txt', header = FALSE)
hams %>%
  select(., V5, V8, V16, V17, V18, V19) %>%
  rename(., callsign = V5, name = V8, address = V16, city = V17, 
         state = V18, zip = V19) %>%
  arrange(., by = callsign) %>%
  knitr::kable(.)
```

# Next steps

1. Normalize the address, city, and zip fields.
2. Automate queries to the FCC database if possible.
3. Expand the range of licensees.
4. Focus on new licensees (last year?)
